Towards a standardized evaluation of imputation methodology

### 2022-09-22 Manuscript/Towards_a_standardized_evaluation_of_imputation_methodology.tex
edit checklist to match ADEMP format

\begin{table}[ht!]
\caption{Checklist for reporting on imputation methodology evaluations.}
\label{table:check}
\begin{tabular}{ll}
% \hline
%   & Suggested aspects to report                                                       \\
\hline
1 & Simulation scope                                                                   \\ \cline{2-2}
$\square$  & Aim                                                                                \\
$\square$  & Design (incl. pseudo-code or flow diagram)                                         \\
$\square$  & Number of simulation repetitions                                                   \\ \hline
2 & Comparative truth                                                                  \\ \cline{2-2}
$\square$  & Data source (model-based or design-based)                                           \\
$\square$  & Sampling variance                                                                  \\
%  & Data characteristics (number of observations, number of variables, variable types, \\
%  & coherence between variables incl. data structures e.g. clustering)                 \\
$\square$  & Data characteristics (incl. multivariate relations and structures e.g. clustering) \\
$\square$  & Estimand                                                                           \\ \hline 
3 & Induced missingness                                                                \\ \cline{2-2}
$\square$  & Missingness mechanism (incl. type or functional form of the missing data   model)  \\
$\square$  & Missingness pattern (incl. missingness proportion)                                 \\ \hline 
4 & Applied methods                                                                    \\ \cline{2-2}
$\square$  & Imputation methods (incl. parameters e.g. the number of imputations)               \\
$\square$  & Analytic methods (incl. calculation of standard errors e.g. pooling   rules)       \\
$\square$  & Reference method (e.g. complete case analysis)                                    \\ \hline 
5 & Imputation evaluation                                                              \\ \cline{2-2}
$\square$  & Imputation-generating process (e.g. algorithmic non-convergence)                   \\
$\square$  & Imputation model fit (e.g. posterior predictive checks)                            \\
$\square$  & Distributional characteristics (e.g. plausibility of imputed values)               \\ \hline 
6 & Performance evaluation                                                             \\ \cline{2-2}
$\square$  & Statistical properties (e.g. confidence validity)                                  \\
$\square$  & Comparative performance (e.g. predictive accuracy)                                 \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[ht!]
\caption{Checklist for reporting on imputation methodology evaluations.}
\label{table:check}
\begin{tabular}{ll}
% \hline
%   & Suggested aspects to report                                                       \\
\hline
1 & Simulation scope                                                                   \\ \cline{2-2}
$\square$  & Aim                                                                                \\
$\square$  & Design (incl. pseudo-code or flow diagram)                                         \\
$\square$  & Number of simulation repetitions                                                   \\ \hline
2 & Data generation                                                                  \\ \cline{2-2}
$\square$  & Data source (e.g. model-based or design-based, sampling variance)                                           \\
%  & Data characteristics (number of observations, number of variables, variable types, \\
%  & coherence between variables incl. data structures e.g. clustering)                 \\
$\square$  & Data characteristics (incl. multivariate relations and structures e.g. clustering) \\
$\square$  & Estimand                                                                           \\ \hline 
3 & Missingness generation                                                                \\ \cline{2-2}
$\square$  & Missingness mechanism (incl. type or functional form of the missing data model)  \\
$\square$  & Missingness pattern (incl. missingness proportions)                                 \\ \hline 
4 & Methods                                                                    \\ \cline{2-2}
$\square$  & Imputation methods (incl. parameters e.g. the number of imputations)               \\
$\square$  & Analytic methods (incl. calculation of standard errors e.g. pooling rules)       \\
$\square$  & Reference methods (e.g. complete case analysis)                                    \\ \hline 
6 & Performance evaluation                                                             \\ \cline{2-2}
$\square$  & Statistical properties (e.g. confidence validity)                                  \\
$\square$  & Comparative performance (e.g. predictive accuracy)                                 \\ \hline
$\square$  & Imputation-generating process (e.g. algorithmic non-convergence)                   \\
$\square$  & Imputation model fit (e.g. posterior predictive checks)                            \\
$\square$  & Distributional characteristics (e.g. plausibility of imputed values)               \\ \hline 
\end{tabular}
\end{table}
